Cosmological constraints from the redshift dependence of the galaxy angular 2-point correlation function

### 2016-10-06 draft/draft0_cris.tex
updates

 %\documentclass[preprint2]{aastex}
%\documentclass[preprint2]{aastex}
%\documentclass[manuscript]{aastex}
\documentclass[iop]{emulateapj}
\renewcommand{\baselinestretch}{0.95}
%% Sometimes a paper's abstract is too long to fit on the
%% title page in preprint2 mode. When that is the case,
%% use the longabstract style option.

@@

@@

%The  Alcock-Paczynski (AP) effect referes to
%the geometric distortion when incorrect cosmological models are assumed for 
%transforming redshift to comoving distance,
%induced by the fact that measured distances along and perpendicular to the line of sight are fundamentally different.

%The AP effect can be measured through the staistial study of galaxies clustering  \citep{Ballinger1996,Matsubara1996,
%Outram2004,Blake2011,ChuangWang2012,Reid2012,Beutler2013,Linder2013,2014arXiv1407.2257S, Jeong2014,Sutter2014,2014ApJ...781...96L,Alam2016, Beutler2016, Sanchez2016},
%symmetry properties of galaxy pairs \citep{Marinoni2010,Jennings2011,BB2012},
%and cosmic voids \citep{Ryden1995,LavausWandelt1995,Sutter2014,Qingqing2016}.
%The main caveat of these methods is that,
%because the radial distances of galaxies are inferred from redshifts,
%AP tests are inevitably limited by redshift-space distortions (RSD) \citep{Ballinger1996},
%which leads to apparent anisotropy even if the adopted cosmology is correct.

%\cite{Li2014,Li2015,Li2016} proposed a novel strategy to measure the redshift dependence of AP.
%Anisotropies produced by the RSD effect are, although large,
%maintaining a nearly uniform magnitude over a large range of redshift,
%while the degree of anisotropies from the AP effect varies with redshift by much larger magnitude. 
%\citep{Li2016} applies this method to the SDSS-III BOSS DR12 galaxies, and obtained tight cosmological constraints 
%comparable to the mainstream probes of SNIa, BAO or CMB.
%This method could play an important role in deriving cosmological constraints from future LSS surveys.

In \cite{Li2014,Li2015,Li2016} we developed a novel strategy to probe $D_A$ and $H$ from LSS data.
%proposed a series of methods to probe the geometric information encoded in the LSS data.
We found fact that the AP or volume effect in general introduces a geometric distortion significantly evolves with redshift;
this phenomenon can be utilized to distinguish the the from the other effects such as the redshift space distortion (RSD).
The radial distances of galaxies are inferred from the measured redshifts which are distorted by the peculiar motion of galaxies, 
leading to apparent distortion in the redshift space galaxy distribution \citep{FOG,Kaiser1987,Ballinger1996}.
It is the major systematic effects limiting our ability to probe the geometry of LSS from galaxy distribution.
We found its influence is significantly reduced in case of studying the redshift dependence of the distortion.

\cite{Li2014} attempted to use the {\it galaxy density gradient field} 
to characterize the redshift evolution of the LSS distortion. 
We tested the idea on Horizon Run 3 (HR3) N-body simulations \citep{horizonrun},
showing the redshift evolution of the statistical property of the gradient field 
can be used to infer unbiased constraints cosmological parameters and is insensitive to RSD.
The same topic was revisited in \cite{Li2015}, 
using the statistical tool of {\it galaxy two-point correlation function} (2pCF) as a function of angle, $\xi(\mu)$, 
where $\mu\equiv \cos \theta$ and $\theta$ is the direction between the connection of the galaxy pairs and the direction.
When incorrect cosmological parameters are adopted, 
the shape of $\xi(\mu)$ is altered due to the anisotropic shape of the LSS (the AP effect), 
and the amplitude is shifted due to the change in the size of comoving volume;
both effects have significant redshift dependence.
The RSD effect, although {\it very significantly} distorts $\xi(\mu)$, 
exhibits less redshift evolution.
The method was applied to BOSS DR12 galaxies \citep{Li2016} to probe the redshift dependent of the AP effect, 
and we come up with tight cosmological constraints comparable to the mainstream probes of SNIa, BAO, CMB and so on.

In this paper we continue our exploration of our strategy and presented 
a new method using the redshift of the shape of {\it galaxy angular 2pCF} as a function of radial scale, $\omega(r_{\bot})$,
to constrain cosmology.
A wrongly adopted cosmology result in {\it redshift-dependent mis-scaling} of the galaxy distribution,
which leads to redshift-evolution of the shape of $\omega(r_{\bot})$.
The signal is sensitive to the cosmological parameters and relatively insensitive to the other effects such as the gravitational growth of structure,
the galaxy bias, and the RSD effect.
We apply our method to the HR4 mock galaxies having hundreds of million galaxies at redshfits 0-2
and develop the statistical procedure to constrain cosmological parameters.

@@

\begin{figure*}
   \centering{
   \includegraphics[height=8cm]{fig1_a.eps}
   \includegraphics[height=8.5cm]{fig1_b.eps}
   }
   \caption{\label{fig_xyquan}
   A description of how wrongly assumed cosmologies can distort the interpretation of observation,
   assuming $\Omega_m=0.26,w=-1$ is the true cosmology. 
   Left panel shows a series of five regular squares, measured by an observer at the origin.
   Their true positions and shapes are plotted in blue dashed lines.
   When the observer adopts the wrong cosmologies to compute the distance from measured redshifts and infer the positions and shapes of the squares,
   he/she obtains distorted squares shown as the red solid lines.
   Right panel shows the redshift evolution of the wrongly estimated angular diameter distance (divided by the correct value).
   }
   % Need a better plot to show angular size variation!!!
\end{figure*}

@@

Mock galaxies are produced from the simulation based on a modified one-to-one correspondence scheme \citep{hong2016}. 
The most bound member particles (MBPs) of simulated halos are adopted as tracers of galaxies.
The merger timescale is computed to get the lifetime of merged halos.
Merger trees of halos are constructed by tracking their MBPs from $z = 12$ to 0;
when a merger event occurs, the merger timescale is computed using the formular of \cite{jiang2008} to 
determine when the satellite galaxy is completely disrupted.
%We modeled the position and the velocity of a galaxy from the position and velocity of its corresponding MBP.
%By using the abundance matching, 
%we modeled the luminosity of a central/isolated galaxies from their current mass
%and of satellite galaxies from their mass at the time of infall.

The resulting mock galaxies was found to reproduce the 2pCF of SDSS DR7 volume-limited galaxy sample \citep{zehavi2011} very well.
The mock galaxies shows a similar finger of god (FOG) feature \citep{FOG} as the observation.
The projected 2pCF of the mock and observational samples agree within 1$\sigma$ CL
on scales greater than 1 ${h^{-1}}$Mpc.

%As will be introduced in the next section, 
%The output of HR4 simulation includes one all-sky light cone mock galaxy catalogue reaching $r=3\,150$ ${h^{-1}}$Mpc 
%and a series ({\bf how many?}) of snapshot mock galaxy catalogues at different redshifts.
We take the snapshot data of the mock galaxies at $z=0,0.5,1,1.5,2$.
%We require subhalos to have at least 30 member particles, 
%so the minimal mass of galaxies is $\simeq m_{p} \simeq 2.7 \times 10^{11} \hMsun$.
Setting a minimal halo mass of $3\times 10^{11} \hMsun$, 
%$4.57\times 10^8$, $4.06\times 10^8$, $3.52\times 10^8$, $3.06\times 10^8$ and $2.28 \times 10^8$ mock galaxies,
we select 457, 406, 352, 206 and 228 million mock galaxies at the five redshifts,
corresponding to a number density of 
%$1.46\times 10^{-2}$, $1.30\times 10^{-2}$, $1.13\times 10^{-2}$, $0.98\times 10^{-2}$ and $0.73\times 10^{-2}\ (h^{-1} \rm Mpc)^{-3}$,
1.46, 1.30, 1.13, 0.98 and 0.73 in unit of $ 10^{-2} h^{3} \rm Mpc^{-3}$,
%$1.46\times 10^{-2}$, $1.30\times 10^{-2}$, $1.13\times 10^{-2}$, $0.98\times 10^{-2}$ and $0.73\times 10^{-2}\ (h^{-1} \rm Mpc)^{-3}$,
respectively.
By applying a uniform mass cut, at higher redshift we have smaller number of galaxies with {\it larger bias}.

@@

When the correct cosmology is adopted the cosmic scale is correctly estimated,
the main factor leads to redshift evolution of galaxy distribution is the gravitational growth of structure.
With the decreasing the redshift, we clearly see the clusters and filaments form and grow.
On the other hand, when the wrong cosmology is adopted, there is an artifical scaling of scales in the constructed map.
The separations among galaxies are over-estimated by 
$25.6\%,47.3\%,62.2\%,71.7\%$ at redshifts of $0.5,1.0,1.5,2.5$,
leading to a clear redshift evolution of sizes of structures.

The growth of structure strengths the clustering and make structures more compact,
while the volume effect maintain the clustering pattern and uniformly re-scale the structures on all scales.
Their imprints on the large scale structure is different and should be distinguishable.
In the following, we show that they affect the angular correlation function measurements in different ways, 
and can be easily separated.

@@

\begin{figure*}
   \centering{
   %\includegraphics[height=5.9cm]{fig8_0.eps}
   %\includegraphics[height=5.9cm]{fig8_wrongcos_0.eps}
   %\includegraphics[width=16cm]{fig2.eps}
   %\includegraphics[width=16cm,natwidth=8,natheight=14]{fig2.pdf}
   \includegraphics[width=16cm]{fig2.eps}
   }
   \caption{\label{fig_scatter}
  The 2D distribution of a $260\times130\times105 (h^{-1}{\rm Mpc})^3$ subsample of HR4 mock galaxies, 
  at redshifts 0.5, 1, 1.5 and 2.
  Left and right panels whos the $x$, $y$ coordinates computed using the ``correct'' parameters $\Omega_m=0.26,\ w=-1$ 
  and a set of wrong cosmological parameters $\Omega_m=0.05,\ w=-1.5$, respectively.
  The growth of structure strengths the clustering and make structures more compact at lower redshift.
  When the wrong cosmology is adopted, the covmoving distances is mis-scaled and over-estimated by $25.6\%,47.3\%,62.2\%,71.7\%$ at redshifts of $0.5,1.0,1.5,2.5$,
  leading to a clear redshift evolution of sizes of structures.
   }
   % Need a better plot to show angular size variation!!!
\end{figure*}

@@

We use the angular 2pCF as a statistical tool to probe the volume effect.
The galaxy 2pCF as a function of galaxy separation in the angular direction, $\omega(r_\perp)$, is computed for snapshot data of mock galaxies at redshifts 0.5, 1, 1.5 and 2.
We adopt the Landy-Szalay estimator~\citep{1993ApJ...412...64L},
\begin{equation}
\omega(r_\perp)=\frac{DD-2DR+RR}{RR}\ ,
\end{equation}
where $DD$ is the number of galaxy--galaxy pairs, 
$DR$ the number of galaxy-random pairs, 
and $RR$ is the number of random--random pairs, 
all separated by a distance defined by $r_\perp\pm\Delta_{r_\perp}$ where we choose $\Delta_{r_\perp}=1h^{-1}\rm Mpc$.
The random catalogue consists of unclustered points uniformly distributed in a same size box. 
In an effort to reduce the statistical variance of the estimator, we use 50 times as many random points as we have galaxies.

Considering the large number of galaxies and random points the 2pCF is computed part by part in subsamples with 
size of 1575 $h^{-1}{\rm Mpc}\times 1575\ h^{-1}{\rm Mpc}\times 105\ h^{-1}{\rm Mpc}$.
The sheet shape of the subsample is close to the shape of redshift shells in the real observational case.
The Z direction with thickness $105\ h^{-1}\rm Mpc$ is treated as the radial direction (the $r$ direction) 
and the X-Y directions %with each of width $1575 h^{-1}\ \rm Mpc$ 
are the angular plane.
For our simulation box size we have 120 such subsamples.
The average of the measurements in all subsamples is adopted as the 2pCF of the whole sample,
while the covariances of them are adopted as the covariance matrix (after multiplying a factor of $1/\sqrt{119}$).

@@

Among different redshifts there is large variation in the amplitude of $\omega(r_\perp)$.
The amplitude is proportional to the clustering strengh which is affected by the gravitational growth of structures and the galaxy bias.
The amplitude is highest at $z=0$ where the structures experienced most growth.
$\omega(r_\perp)$ also increases with redshift at $z>1$ with increasing redshift 
as a reason of increasing galaxy bias.
%leading to stronger clustering strength and higher amplitude of 2pCF.
%On the contrary, at higher redshift we find $\omega(z=2)>\omega(z=1.5)>\omega(z=1)$,
%The trend is different from $z=1,1.5,2$,
%simply because by applying a uniform mass cut we are selecting more biased galaxies at higher redshift.

Different from the large variation of amplitude among different redshifts, 
%The shape of $r_\perp\omega$ also evolves with redshift.
the shape of $r_\perp\omega$ maintains similar at all redshifts;
in general it peaks at $r\sim9 h^{-1}\rm Mpc$ and monotonically drops or increases at larger or smaller scales.
The only exception is the small enhancement at $r\lesssim 2 h^{-1}\rm Mpc$,
which is caused by the non-linear growth of structures 
and is much more significant at lower redshfit.

In order to directly compare the shape of 2pCF at different redshifts,
in the middle panel of Figure \ref{fig_diffz} 
we show the $r_\perp\omega$ normalized by the overall amplitude within 
$5h^{-1}{\rm Mpc} < r < 40h^{-1}{\rm Mpc}$
(here after $\hat \omega_{r_\perp}$):
\begin{equation}
 \hat \omega_{ r_\perp} \equiv  \frac{ {r_\perp\omega}(r_{\perp})}{ \int_{r_{\perp, \rm min}}^{r_{\perp, \rm max}}r_{\perp} \omega(r_{\perp}) d r_{\perp} / (r_{\perp,\rm max}-r_{\perp,\rm min}) },
\end{equation}
where we choose $r_{\perp, \rm min}=5 h^{-1}$ Mpc, $r_{\perp, \rm max}=40 h^{-1}$ Mpc in this analysis.
Below $5 h^{-1}$ Mpc the non-linear growth of structure 
leads to systematic redshift evolution which could be difficult to be reliably accounted;
On scales larger than $40 h^{-1}$ Mpc,
the analytical modelling of the shape of the angular 2pCF is relatively well understood;
one can just fit the 2pCF with the theoretical predictions \citep{Salvador2014,Salvador2016} 
instead of using our method 
(although out method should is also applicable).

In the upper-middle panel, the nice overlapping of the $\hat\omega_{r_\perp}$
more clearly shows the the small redshift evolution of the shape.
In the upper-right panel, 
we further show the residual evolution at high redshifts 
with respect to $z=0$.
There is only 1-4\% enhancement 
at $r<10h^{-1}\rm Mpc$,
and $<1.5\%$ suppression at $r>25 h^{-1}\rm Mpc$.
The trend is monotonic with redshift.

There is one detail in the analysis which should be emphasized here.
In real observations we are observing {\it different} objects in different redshift shells.
Considering this fact in the comparison of $\hat\omega_{r_\perp}$ 
we compare subsamples of galaxies at {\it different} locations.
As an exammple, if at $z=0$ we take $\hat\omega_{r_\perp}$ measured within $0h^{-1}{\rm Mpc}<Z<105 h^{-1}{\rm Mpc}$,
at higher redshifts we then adopt measurement within $105h^{-1}{\rm Mpc}<Z<210 h^{-1}{\rm Mpc}$ for a comparision.
%and take the difference between them to get $\delta \hat{r_\perp\omega}$.
%So we are always comparing 2pCF measured from different samples of galaxies.
If simply comparing the 2pCF of a {\it same} subsample of galaxies at different redshifts, 
one would significantly underestimate the statistical undertainty of $\delta \hat{\omega}_{r_\perp}$ by ignoring the cosmic variance.
%The error bars and covariance are always estimated in this way to take the cosmic variance into consideration.
%\footnote{In all figures of this paper The error bars displayed in all figures are estimated in this way; 
%from the 120 subsamples and for the error bar of redshift evolution of 2pCF 
%we always take the cosmic variance into consideration.}.

@@

The angular 2pCF of galaxy positions constructed in a wrong cosmology $\Omega_m=0.05,\ w=-1.5$
is displayed in the lower panels of Figure \ref{fig_diffz}.
The mis-scaling uniformly shifts clustering patterns on all scales, 
leading to a wrong $\hat \omega_{r_\perp}$ 
related with the correct one as
\begin{equation}
 \hat \omega_{r_\perp,\rm wrong}(r) = \hat \omega_{r_\perp, \rm correct}(\alpha_{\perp} r),
\end{equation}
a simple consequence of the fact that clustering patterns at scale $r$ is rescaled to $\alpha_{\perp} r$.
The redshift evolution of $\alpha_{\perp}$ leads to redshift evolution of 
$\hat \omega_{r_\perp, \rm correct}$,
%Lower panels of Figure \ref{fig_diffz} shows the $r_\perp\omega$ in five 
%snapshots, in case that the cosmology $\Omega_m=0.05,\ w=-1.5$ 
%is adopted to construct the galaxy distribution (the right panels of Figure \ref{fig_scatter}).
which is displayed in the lower-middle panel.
The upscaling of comoving distance leads to a stretched shape.
With the increasing of redshift,
the peak location is shifted from $9h^{-1} \rm Mpc$ to $15 h^{-1}\rm Mpc$ at $z=2$,
as a result of the fact that the angular separation is upscaled by $71.7\%$.
Correspondingly, the right panel shows that, 
compared with $\hat \omega_{r_\perp}$ at $z=0$ there is a 20-40\% change at higher redshifts.

@@

Sec. \ref{sec_2pCF_diffz} shows that $\hat \omega_{r_\perp}$ measured from 
constant mass cut samples at different redshifts is close to each other.
The gravitational growth of structure will not have large impact on $\hat \omega_{r_\perp}$ on scales $\gtrsim5 h^{-1}$ Mpc.
Yet there are many other factors may introduce redshift evolution,
including galaxy bias, RSD, redshift error, and 
the redshift evolution of properties of galaxies 
such as the mass, morphology, color, concentration, and so on. 
Here we test two ``major'' systematical effects, the galaxy bias and the RSD effect.

@@

Galaxies are biased tracers of dark matter field;
more massive galaxies reside in regions with higher density contrast
and exhibit stronger clustering (i.e. larger bias).
%In large scale structure surveys, the bias of the galaxy sample is an important fator affecting on the clustering properties of the sample.

>>>>

 %\documentclass[preprint2]{aastex}
%\documentclass[preprint2]{aastex}
%\documentclass[manuscript]{aastex}
\documentclass[iop]{emulateapj}
\usepackage{color}
\renewcommand{\baselinestretch}{0.95}
%% Sometimes a paper's abstract is too long to fit on the
%% title page in preprint2 mode. When that is the case,
%% use the longabstract style option.

@@

\newcommand{\scr}{\textcolor{red}}

@@

In \cite{Li2014,Li2015,Li2016} we developed a novel strategy to probe $D_A$ and $H$ from LSS data.
%proposed a series of methods to probe the geometric information encoded in the LSS data.
We found fact that the AP or volume effect in general introduces a geometric distortion that evolves significantly with redshift;
this phenomenon can be utilized to distinguish the \scr{AP effect(?)} the from the other effects such as the redshift space distortion (RSD).
The radial distances of galaxies are inferred from the measured redshifts, which are distorted by the peculiar motion of galaxies, 
leading to apparent distortion in the redshift space galaxy distribution \citep{FOG,Kaiser1987,Ballinger1996}.
It is the major systematic effects limiting our ability to probe the geometry of LSS from galaxy distribution.
We found its influence is significantly reduced in case of studying the redshift dependence of the distortion.

\cite{Li2014} attempted to use the {\it galaxy density gradient field} 
to characterize the redshift evolution of the LSS distortion. 
We tested the idea on the Horizon Run 3 (HR3) N-body simulations \citep{horizonrun},
showing the redshift evolution of the statistical property of the gradient field 
can be used to infer unbiased constraints on certain cosmological parameters and that it is, largely, insensitive to RSD.
The same topic was revisited in \cite{Li2015}, 
using a slightly modified version of the usual anisotropic galaxy two-point correlation function (2pCF), $\xi(\mu)$, 
where $\mu\equiv \cos \theta$ and $\theta$ is the direction between the connection of the galaxy pairs and the direction.
When an incorrect cosmological model is adopted, 
the shape of $\xi(\mu)$ is altered due to the anisotropic distortion of the LSS (the AP effect), 
and the amplitude is shifted due to the change in the comoving volume elements;
both effects have significant redshift dependence.
The RSD effect, significantly distorts $\xi(\mu)$, however it
exhibits much less redshift evolution.
The method was applied to BOSS DR12 galaxies \citep{Li2016} to probe the redshift dependent of the AP effect, 
and we come up with tight cosmological constraints comparable to the mainstream probes of SNIa, BAO, CMB and so on.

In this paper we continue our exploration of our strategy and presented 
a new method using the redshift of the shape of the {\it galaxy angular 2pCF} as a function of radial scale, $\omega(r_{\bot})$,
to constrain cosmology.
A wrongly adopted cosmology result in {\it redshift-dependent mis-scaling} of the galaxy distribution,
which leads to redshift-evolution of the shape of $\omega(r_{\bot})$.
The signal is sensitive to the cosmological parameters and relatively insensitive to the other effects such as the gravitational growth of structure,
the galaxy bias, and the RSD effect.
We apply our method to the HR4 mock galaxies having hundreds of million galaxies at redshfits 0-2
and develop the statistical procedure to constrain cosmological parameters.

@@

\begin{figure*}
   \centering{
   \includegraphics[height=8cm]{fig1_a.eps}
   \includegraphics[height=8.5cm]{fig1_b.eps}
   }
   \caption{\label{fig_xyquan}
   A description of how incorrectly assumed cosmologies can distort the interpretation of observation,
   assuming $\Omega_m=0.26,w=-1$ is the true cosmology. 
   Left panel shows a series of five regular squares, measured by an observer at the origin.
   Their true positions and shapes are plotted in blue dashed lines.
   When the observer adopts the wrong cosmologies to compute the distance from measured redshifts and infer the positions and shapes of the squares,
   he/she obtains distorted squares shown as the red solid lines.
   Right panel shows the redshift evolution of the wrongly estimated angular diameter distance (divided by the correct value).
   }
   % Need a better plot to show angular size variation!!!
\end{figure*}

@@

Mock galaxies are produced from the simulation based on a modified one-to-one correspondence scheme \citep{hong2016}. 
The most bound member particles (MBPs) of simulated halos are adopted as tracers of galaxies.
The merger timescale is computed to obtain the lifetime of merged halos.
Merger trees of halos are constructed by tracking their MBPs from $z = 12$ to 0;
when a merger event occurs, the merger timescale is computed using the formula of \cite{jiang2008} to 
determine when the satellite galaxy is completely disrupted.
%We modeled the position and the velocity of a galaxy from the position and velocity of its corresponding MBP.
%By using the abundance matching, 
%we modeled the luminosity of a central/isolated galaxies from their current mass
%and of satellite galaxies from their mass at the time of infall.

The resulting mock galaxies were found to reproduce the 2pCF of the SDSS DR7 volume-limited galaxy sample \citep{zehavi2011} very well.
The mock galaxies shows a similar finger of god (FOG) feature \citep{FOG} as the observation.
The projected 2pCF of the mock and observational samples agree within 1$\sigma$ CL
on scales greater than 1 ${h^{-1}}$Mpc.

%As will be introduced in the next section, 
%The output of HR4 simulation includes one all-sky light cone mock galaxy catalogue reaching $r=3\,150$ ${h^{-1}}$Mpc 
%and a series ({\bf how many?}) of snapshot mock galaxy catalogues at different redshifts.
We take the snapshot data of the mock galaxies at $z=0,0.5,1,1.5,2$.
%We require subhalos to have at least 30 member particles, 
%so the minimal mass of galaxies is $\simeq m_{p} \simeq 2.7 \times 10^{11} \hMsun$.
Setting a minimal halo mass of $3\times 10^{11} \hMsun$, 
%$4.57\times 10^8$, $4.06\times 10^8$, $3.52\times 10^8$, $3.06\times 10^8$ and $2.28 \times 10^8$ mock galaxies,
we select 457, 406, 352, 206 and 228 million mock galaxies at the five redshifts,
corresponding to a number density of 
%$1.46\times 10^{-2}$, $1.30\times 10^{-2}$, $1.13\times 10^{-2}$, $0.98\times 10^{-2}$ and $0.73\times 10^{-2}\ (h^{-1} \rm Mpc)^{-3}$,
1.46, 1.30, 1.13, 0.98 and 0.73 in unit of $ 10^{-2} h^{3} \rm Mpc^{-3}$,
%$1.46\times 10^{-2}$, $1.30\times 10^{-2}$, $1.13\times 10^{-2}$, $0.98\times 10^{-2}$ and $0.73\times 10^{-2}\ (h^{-1} \rm Mpc)^{-3}$,
respectively.
Applying a uniform mass cut, at higher redshift we obtained a smaller number of galaxies with {\it larger bias}.

@@

\scr{When the correct cosmology is adopted the cosmic scale is correctly estimated,
the main factor leads to redshift evolution of galaxy distribution is the gravitational growth of structure.
With the decreasing the redshift, we clearly see the clusters and filaments form and grow.
On the other hand, when the wrong cosmology is adopted, there is an artificial scaling of scales in the constructed map.
The separations among galaxies are over-estimated by 
$25.6\%,47.3\%,62.2\%,71.7\%$ at redshifts of $0.5,1.0,1.5,2.5$,
leading to a clear redshift evolution of sizes of structures.}

The growth of structure enhances the clustering and results in more compact structures,
while the volume effect maintains the clustering pattern and uniformly re-scales the structures on all scales.
The imprint of each of these effects on the large scale structure is different and should be distinguishable.
In the following section we show that they affect the angular correlation function measurements in different ways, 
and thus can be easily separated.

@@

\begin{figure*}
   \centering{
   %\includegraphics[height=5.9cm]{fig8_0.eps}
   %\includegraphics[height=5.9cm]{fig8_wrongcos_0.eps}
   %\includegraphics[width=16cm]{fig2.eps}
   %\includegraphics[width=16cm,natwidth=8,natheight=14]{fig2.pdf}
   \includegraphics[width=16cm]{fig2.eps}
   }
   \caption{\label{fig_scatter}
  The 2D distribution of a $260\times130\times105 (h^{-1}{\rm Mpc})^3$ subsample of HR4 mock galaxies, 
  at redshifts 0.5, 1, 1.5 and 2.
  Left and right panels show the $x$, $y$ coordinates computed using the ``correct'' parameters $\Omega_m=0.26,\ w=-1$ 
  and a set of wrong cosmological parameters $\Omega_m=0.05,\ w=-1.5$, respectively.
  The growth of structure strengths the clustering and make structures more compact at lower redshift.
  When the wrong cosmology is adopted, the covmoving distances are mis-scaled and over-estimated by $25.6\%,47.3\%,62.2\%,71.7\%$ at redshifts of $0.5,1.0,1.5,2.5$, respectively,  leading to a clear redshift evolution of the sizes of structures.
   }
   % Need a better plot to show angular size variation!!!
\end{figure*}

@@

We use the angular 2pCF as a statistical tool to probe the volume effect.
The galaxy 2pCF as a function of galaxy separation in the angular direction, $\omega(r_\perp)$, is computed for snapshot data of mock galaxies at redshifts 0.5, 1, 1.5 and 2.
We adopt the Landy-Szalay estimator~\citep{1993ApJ...412...64L},
\begin{equation}
\omega(r_\perp)=\frac{DD-2DR+RR}{RR}\ ,
\end{equation}
where $DD$ is the number of galaxy--galaxy pairs, 
$DR$ the number of galaxy-random pairs, 
and $RR$ is the number of random--random pairs, 
all separated by a distance defined by $r_\perp\pm\Delta_{r_\perp}$ where we choose $\Delta_{r_\perp}=1h^{-1}\rm Mpc$.
The random catalogue consists of unclustered points uniformly distributed in the same space as the simulated data.. 
In an effort to reduce the statistical variance of the estimator, we use 50 times as many random points as we have galaxies.

Considering the large number of galaxies and random points the 2pCF is computed part by part in subsamples with 
size of 1575 $h^{-1}{\rm Mpc}\times 1575\ h^{-1}{\rm Mpc}\times 105\ h^{-1}{\rm Mpc}$.
The `sheet'-like shape of the subsample is similar to the shape of redshift shells in the real observational case.
The Z direction with thickness $105\ h^{-1}\rm Mpc$ is treated as the radial direction (the $r$ direction) 
and the X-Y directions %with each of width $1575 h^{-1}\ \rm Mpc$ 
are the angular plane.
For our simulation box size we have 120 such subsamples.
The average of the measurements in all subsamples is taken as the 2pCF of the whole sample,
while the covariances of them are taken to be the covariance matrix (after multiplying a factor of $1/\sqrt{119}$).

@@

Among different redshifts there is large variation in the amplitude of $\omega(r_\perp)$.
The amplitude is proportional to the clustering strength, which is affected by the gravitational growth of structures and the galaxy bias.
The amplitude is highest at $z=0$ where the structures experienced most growth.
$\omega(r_\perp)$ also increases with redshift at $z>1$ with increasing redshift 
as a reason of increasing galaxy bias.
%leading to stronger clustering strength and higher amplitude of 2pCF.
%On the contrary, at higher redshift we find $\omega(z=2)>\omega(z=1.5)>\omega(z=1)$,
%The trend is different from $z=1,1.5,2$,
%simply because by applying a uniform mass cut we are selecting more biased galaxies at higher redshift.

Apart from the large variation in amplitude between the different redshifts bins, 
%The shape of $r_\perp\omega$ also evolves with redshift.
the shape of $r_\perp\omega$  is similar at all redshifts;
in general it peaks at $r\sim9 h^{-1}\rm Mpc$ and monotonically drops or increases at larger or smaller scales.
The only exception is the small enhancement at $r\lesssim 2 h^{-1}\rm Mpc$,
which is caused by the non-linear growth of structures 
and is much more significant at lower redshift.

In order to directly compare the shape of 2pCF at different redshifts,
in the middle panel of Figure \ref{fig_diffz} 
we show the $r_\perp\omega$ normalized by the overall amplitude within 
$5h^{-1}{\rm Mpc} < r < 40h^{-1}{\rm Mpc}$
(here after $\hat \omega_{r_\perp}$):
\begin{equation}
 \hat \omega_{ r_\perp} \equiv  \frac{ {r_\perp\omega}(r_{\perp})}{ \int_{r_{\perp, \rm min}}^{r_{\perp, \rm max}}r_{\perp} \omega(r_{\perp}) d r_{\perp} / (r_{\perp,\rm max}-r_{\perp,\rm min}) },
\end{equation}
where we choose $r_{\perp, \rm min}=5 h^{-1}$ Mpc, $r_{\perp, \rm max}=40 h^{-1}$ Mpc in this analysis.
Below $5 h^{-1}$ Mpc the non-linear growth of structure 
leads to systematic redshift evolution which could be difficult to be reliably accounted;
On scales larger than $40 h^{-1}$ Mpc,
the analytical modelling of the shape of the angular 2pCF is relatively well understood;
one can just fit the 2pCF with the theoretical predictions \citep{Salvador2014,Salvador2016} 
instead of using our method 
(although our method should also be applicable).

In the upper-middle panel, the overlapping $\hat\omega$'s
clearly show the minimal redshift evolution of the shape.
In the upper-right panel, 
we further show the residual evolution at high redshifts 
with respect to $z=0$.
There is only 1-4\% enhancement 
at $r<10h^{-1}\rm Mpc$,
and $<1.5\%$ suppression at $r>25 h^{-1}\rm Mpc$.
The trend is monotonic with redshift.

There is one detail in the analysis that should be emphasized here.
In real observations we may be selecting {\it different} types of galaxies at different redshifts.
Considering this fact in the comparison of $\hat\omega_{r_\perp}$ 
we compare subsamples of galaxies at {\it different} locations.
As an example, if at $z=0$ we take $\hat\omega_{r_\perp}$ measured within $0h^{-1}{\rm Mpc}<Z<105 h^{-1}{\rm Mpc}$,
at higher redshifts we then adopt measurement within $105h^{-1}{\rm Mpc}<Z<210 h^{-1}{\rm Mpc}$ for a comparison.
%and take the difference between them to get $\delta \hat{r_\perp\omega}$.
%So we are always comparing 2pCF measured from different samples of galaxies.
If we simply compare the 2pCF of the {\it same} subsample of galaxies at different redshifts, 
one would significantly underestimate the statistical uncertainty of $\delta \hat{\omega}_{r_\perp}$ by ignoring the cosmic variance.
%The error bars and covariance are always estimated in this way to take the cosmic variance into consideration.
%\footnote{In all figures of this paper The error bars displayed in all figures are estimated in this way; 
%from the 120 subsamples and for the error bar of redshift evolution of 2pCF 
%we always take the cosmic variance into consideration.}.

@@

The angular 2pCF of galaxy positions constructed in a wrongly assumed cosmology $\Omega_m=0.05,\ w=-1.5$
is displayed in the lower panels of Figure \ref{fig_diffz}.
The mis-scaling uniformly shifts the clustering pattern on all scales, 
leading to a biased $\hat \omega_{r_\perp}$, which is 
related with the true $\hat \omega$ as
\begin{equation}
 \hat \omega_{r_\perp,\rm wrong}(r) = \hat \omega_{r_\perp, \rm correct}(\alpha_{\perp} r),
\end{equation}
a simple consequence of the fact that the clustering pattern at scale $r$ is rescaled to $\alpha_{\perp} r$.
The redshift evolution of $\alpha_{\perp}$ leads to redshift evolution of 
$\hat \omega_{r_\perp, \rm correct}$,
%Lower panels of Figure \ref{fig_diffz} shows the $r_\perp\omega$ in five 
%snapshots, in case that the cosmology $\Omega_m=0.05,\ w=-1.5$ 
%is adopted to construct the galaxy distribution (the right panels of Figure \ref{fig_scatter}).
which is displayed in the lower-middle panel.
The upscaling of comoving distance leads to a stretched shape.
When increasing redshift,
the peak location is shifted from $\sim9h^{-1} \rm Mpc$ to $\sim15 h^{-1}\rm Mpc$ at $z=2$,
as a result of the fact that the angular separation is upscaled by $71.7\%$.
Correspondingly, the right panel shows that, 
compared with $\hat \omega_{r_\perp}$ at $z=0$ there is a 20-40\% change at higher redshifts.

@@

In Sec. \ref{sec_2pCF_diffz} we showed that $\hat \omega_{r_\perp}$ measured from the
constant mass cut samples at different redshifts are relatively close to each other.
The gravitational growth of structure will not have a large impact on $\hat \omega_{r_\perp}$ on scales $\gtrsim5 h^{-1}$ Mpc.
Yet there are many other factors that may induce redshift evolution,
including galaxy bias, RSD, redshift error, and 
the redshift evolution of galaxies properties 
such as mass, morphology, color, concentration, and so on. 
Here we test two ``major'' systematical effects; the galaxy bias and the RSD effect.

@@

Galaxies are biased tracers of the dark matter field;
more massive galaxies reside in regions with higher density contrast
and exhibit stronger clustering (i.e. larger bias).
%In large scale structure surveys, the bias of the galaxy sample is an important fator affecting on the clustering properties of the sample.

We vary the mass cut and check the effect of galaxy bias on $\hat \omega_{r_\perp}$.
The upper panels of Figure \ref{fig_sys} displays the 2pCF measured from galaxies within a $3175\times3175\times105$ $(h^{-1}\rm Mpc)^3$ volume, taken from the $z=0$ snapshot.
Four values of minimal mass limits, $3\times 10^{11} M_{\odot}$, $1\times 10^{12} M_{\odot}$, $4\times 10^{12} M_{\odot}$ and $1\times 10^{13} M_{\odot}$,
are imposed to create three \scr{four?} samples with different galaxy bias.
The measured angular 2pCF are displayed.
